---
title: "Introduction to Sgpv"
author: "Mengxi Wei"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Sgpv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__Sgpv__ is a simple R package developed to select variables with second-generation p-values. Four functions are considered, _sgpv_, _print.sgpv_, _coef.sgpv_, _summary.sgpv_. All functions are given for variable selection with second-generation p-values method.

## Second-Generation P-Values
Let $\theta$ as a parameter of interest: $I=[\theta_l,\theta_u]$

Interval null: $H_0=[-\delta,\delta]$

Second-Generation P-Values can be defined as

$$p_{\delta}=\frac{|I\cap H_0|}{|I|}\times {\rm max}\left\{\frac{|I|}{2|H_0|},1\right\}$$

## Solution

$S=\left\{k \in C:|\hat{\beta}^{{\rm ols}}_k|>\lambda_k\right\}$

$C$ is the initial set of variables for coming selection. Here we choose 95% CI, so $\lambda_k=1.96\times {\rm SE}_k+\overline{\rm SE}$.

## The source R code for _sgpv_:

Standardize inputs in linear regression 
and the inputs can be variables which have been selected from other methods like lasso.

```{r,eval=FALSE}
sgpv <- function(x, y) {
  if (!is.numeric(as.matrix(x)) | !is.numeric(y)) 
    stop("The input data have non-numeric values.")
  if (any(complete.cases(x) == F) | any(complete.cases(y) == F)) {
    warning("Only complete records will be used.\n")
    comp.index <- complete.cases(data.frame(x, y))# delete invalid data
    x <- x[comp.index, ]
    y <- y[comp.index, ]
  }
  xs <- scale(x)
  ys <- scale(y)
  mod <- lm(ys ~ xs)
  pe <- summary(mod)$coef[-1, 1]
  se <- summary(mod)$coef[-1, 2]

  candidate.index <- 1:ncol(xs)
  null.bound.p <- mean(se)
  out.sgpv <- candidate.index[which(abs(pe) > 1.96 * se + null.bound.p)]
  pe.can <- pe
  lb.can <- pe - 1.96 * se
  ub.can <- pe + 1.96 * se

  out <- list(
    var.index = out.sgpv,
    var.label = colnames(x)[out.sgpv],
    x = data.frame(x),
    y = y,
    pe.can = pe.can,
    lb.can = lb.can,
    ub.can = ub.can,
    null.bound.p = null.bound.p
  )
  
  class(out) <- "sgpv"
  return(out)
}
```

## The source R code for _print.sgpv_:
```{r,eval=FALSE}
print.sgpv <- function(object, ...) {
  out.coef <- numeric(ncol(object$x))
  if (length(object$var.index) > 0) {
    data.d <- data.frame(yy = object$y, 
                         xx = object$x[, object$var.index])
    out.sgpv.coef <- coef(lm(yy ~ ., data = data.d))[-1]
    for (i in 1:length(object$var.index)) {
      out.coef[object$var.index[i]] <- out.sgpv.coef[i]
    }
  }
  if (length(object$var.index) > 0) {
    cat("Selected variables are", object$var.label, "\n")
  } else {
    cat("None of variables are selected.\n")
  }
  out <- list(object$var.label, out.coef)
  return(out)
}
```

## The source R code for _summary.sgpv_:
```{r,eval=FALSE}
summary.sgpv <- function(object, ...) {
  if (length(object$var.index) > 0){
    data.d <- data.frame(yy = object$y, 
                         xx = object$x[, object$var.index])
    colnames(data.d)[1] <- "Response"
    colnames(data.d)[-1] <- object$var.label
    summary(lm(Response ~ 1, data = data.d))
  } else {
    message("None of variables are selected.")
    message("Therefore, the summary is shown for the model with intercept only\n")
  }
  data.d <- data.frame(yy = object$y)
  colnames(data.d)[1] <- "Response"
  summary(lm(Response ~ 1, data = data.d))
}
```